---
title: "EDA"
editor: visual
execute:
  echo: false
  warning: false
---

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
library(tidyverse)
library(randomForest)
library(caret)
library(corrplot)
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false

df <- read_csv("data.csv")
df$time <- as.POSIXct(df$time, format = "%Y-%m-%d %H:%M:%S")
df <- df[, -10]

features <- select(df, -time)
labels <- df$temperature


set.seed(123)
train_indices <- createDataPartition(labels, p = 0.7, list = FALSE)
train_features <- features[train_indices, ]
train_labels <- labels[train_indices]
test_features <- features[-train_indices, ]
test_labels <- labels[-train_indices]

train <- data.frame(train_features, temperature = train_labels)


```

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
train
```



```{r}
ggplot(df, aes(x = temperature)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black", alpha = 0.5) +
  labs(x = "Temperature", y = "Frequency", title = "Distribution of Temperature") +
  theme_minimal()

```

*This histogram illustrates the distribution of temperature values in the dataset. It shows how frequently different temperature ranges occur, helping to understand the central tendency and spread of temperature measurements.*

```{r}
library(forecast)
df_ts <- ts(df$temperature, frequency = 7)  
decomposed <- decompose(df_ts)
autoplot(decomposed) + labs(title = "Time Series Decomposition of Temperature")


```

*The decomposition plot breaks down the temperature data into its seasonal, trend, and residual components. This helps in identifying patterns over time, such as recurring seasonal variations or long-term trends in temperature changes.*

```{r}
graph2 <- ggplot(df, aes(x = time, y = temperature)) +
  geom_bar(stat = 'identity', color = 'steelblue', alpha = 0.8) +  # Adjust appearance of bars
  scale_fill_brewer(palette = "Set3") +  # Color palette for bars
  labs(
    title = "Temperature Over Time",
    x = "Time",
    y = "Temperature (°C)"
  ) +
  theme_minimal() +  # Use minimal theme
  theme(legend.position = "none")  # Remove legend for fill color

print(graph2)
```


*This bar plot visualizes how temperature varies over time, using timestamps (time) and corresponding temperature values. Each bar represents a specific time period, providing a clear overview of how temperatures fluctuate across different time points.*