---
title: "Predictions"
author: "Ghost"
date: "2024-07-10"
output: html_document
execute:
  echo: false
  warning: false

---

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
library(tidyverse)
library(randomForest)
library(caret)
library(corrplot)
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false

df <- read_csv("data.csv")
df$time <- as.POSIXct(df$time, format = "%Y-%m-%d %H:%M:%S")
df <- df[, -10]

features <- select(df, -time)
labels <- df$temperature


set.seed(123)
train_indices <- createDataPartition(labels, p = 0.7, list = FALSE)
train_features <- features[train_indices, ]
train_labels <- labels[train_indices]
test_features <- features[-train_indices, ]
test_labels <- labels[-train_indices]

train <- data.frame(train_features, temperature = train_labels)


```

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
train
```



```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
sum(is.na(train$particle1))

sum(is.na(train_labels))

sum(is.na(train_features))

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
df$particle1[is.na(df$particle1)] <- mean(df$particle1, na.rm = TRUE)
df$particle2[is.na(df$particle2)] <- mean(df$particle2, na.rm = TRUE)
df$particle3[is.na(df$particle3)] <- mean(df$particle3, na.rm = TRUE)

train$particle1[is.na(train$particle1)] <- mean(train$particle1, na.rm = TRUE)
train$particle2[is.na(train$particle2)] <- mean(train$particle2, na.rm = TRUE)
train$particle3[is.na(train$particle3)] <- mean(train$particle3, na.rm = TRUE)


train_features$particle1[is.na(train_features$particle1)] <- mean(train_features$particle1, na.rm = TRUE)
train_features$particle2[is.na(train_features$particle2)] <- mean(train_features$particle2, na.rm = TRUE)
train_features$particle3[is.na(train_features$particle3)] <- mean(train_features$particle3, na.rm = TRUE)
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
rf_model <- randomForest(train_labels ~ ., data = train_features, ntree = 500)

rf_model

```

```{r}

imporctance <- varImpPlot(rf_model)
```
*This plot displays the importance of each predictor variable in the random forest model. It helps identify which features (such as humidity, speed, etc.) have the most significant influence on predicting temperature.*


```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
predictions <- predict(rf_model, newdata = test_features)

predictions[is.na(predictions)] <- mean(predictions, na.rm = TRUE)
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
mae <- mean(abs(predictions - test_labels))
cat("Mean Absolute Error (MAE):", mae, "\n")

mape <- mean(abs(predictions - test_labels) / test_labels) * 100
accuracy <- 100 - mape
cat("Accuracy:", accuracy, "%\n")

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
library(ggplot2)


plot_data <- data.frame(
  Actual = test_labels,
  Predicted = predictions
)


plot1 <- ggplot(plot_data, aes(x = Actual, y = Predicted)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "blue") + 
  labs(x = "Actual Temperature", y = "Predicted Temperature", title = "Actual vs. Predicted Temperature") +
  theme_minimal()

```

*This scatter plot compares the actual temperature values with the predicted values from the random forest model. The dashed line represents perfect prediction, where actual equals predicted temperature.*

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
plot2 <- ggplot(plot_data, aes(x = Actual, y = Actual - Predicted)) +
  geom_point() +
  labs(x = "Actual Temperature", y = "Residual", title = "Residual Plot")

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false

plot_data <- data.frame(
  Actual = test_labels,   
  Predicted = predictions 
)

plot_data$index <- seq_along(test_labels)

ggplot(plot_data, aes(x = index)) +
  geom_line(aes(y = Actual, color = "Actual")) + 
  geom_line(aes(y = Predicted, color = "Predicted")) +  
  scale_color_manual(name = "Series", values = c(Actual = "blue", Predicted = "red")) + 
  labs(x = "Size", y = "Temperature", title = "Actual vs. Predicted Temperature") + 
  theme_minimal()

```
```{r}
plot1
```

```{r}
plot2
```
*This plot shows the residuals (difference between actual and predicted temperatures) against the actual temperatures. It helps assess the model's performance and detect any patterns in prediction errors.*


```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
# Simulate different scenarios for next week
num_days <- 7
new_data <- data.frame(
  temperature = rep(NA, num_days),
  humidity = rep(NA, num_days),
  speed = rep(NA, num_days),
  rain = rep(NA, num_days),
  pressure = rep(NA, num_days),
  particle1 = rep(NA, num_days), 
  particle2 = rep(NA, num_days), 
  particle3 = rep(NA, num_days)
)

# Simulate different scenarios for each day
for (day in 1:num_days) {
  new_data$temperature[day] <- mean(train$temperature, na.rm = TRUE) + rnorm(1, mean = 0, sd = 3)
  new_data$humidity[day] <- mean(train$humidity, na.rm = TRUE) + rnorm(1, mean = 0, sd = 5)
  new_data$speed[day] <- mean(train$speed, na.rm = TRUE) + rnorm(1, mean = 0, sd = 2)
  new_data$rain[day] <- mean(train$rain, na.rm = TRUE) + rnorm(1, mean = 0, sd = 1)
  new_data$pressure[day] <- mean(train$pressure, na.rm = TRUE) + rnorm(1, mean = 0, sd = 3)
  new_data$particle1[day] <- mean(train$particle1, na.rm = TRUE) + rnorm(1, mean = 0, sd = 0.5)
  new_data$particle2[day] <- mean(train$particle2, na.rm = TRUE) + rnorm(1, mean = 0, sd = 0.5)
  new_data$particle3[day] <- mean(train$particle3, na.rm = TRUE) + rnorm(1, mean = 0, sd = 0.5)
}

# Predict temperatures for next week


```

```{r}
# Predict temperatures for next week
predictions_next_week <- predict(rf_model, newdata = new_data)
predictions_next_week

```


```{r}
# Set the starting date to February 23, 2022
start_date <- as.Date("2022-02-23")

# Generate dates for the next week
dates_next_week <- seq(start_date, by = "day", length.out = 7)

# Prepare data for plotting
plot_data_next_week <- data.frame(
  Date = dates_next_week,
  Predicted_Temperature = predictions_next_week
)

# Plot predicted temperatures for next week
ggplot(plot_data_next_week, aes(x = Date, y = Predicted_Temperature)) +
  geom_line(color = "blue") +
  geom_point(color = "blue") +
  labs(x = "Date", y = "Predicted Temperature", title = "Predicted Temperatures for Next Week") +
  theme_minimal()

```

*This line plot predicts temperatures for the next week based on the trained random forest model. It helps users anticipate temperature trends for planning purposes.*





```{r}
df$time <- as.POSIXct(df$time)


plot_data <- data.frame(
  hour = df$time,
  Actual_Temperature = df$temperature,
  Predicted_Temperature = c(rep(NA, nrow(df) - 7), predictions_next_week)
)


ggplot(plot_data, aes(x = hour)) +
  geom_line(aes(y = Actual_Temperature, color = "Actual")) +
  geom_line(aes(y = Predicted_Temperature, color = "Predicted"), linetype = "dashed") +
  labs(x = "Date", y = "Temperature", title = "Actual vs. Predicted Temperature") +
  scale_color_manual(name = "Series", values = c("Actual" = "blue", "Predicted" = "red")) +
  theme_minimal()

```

*This plot compares hourly actual temperatures with predicted temperatures, including predictions for the next week. It provides a detailed view of model performance over time.* 


